---
title: "The apiFetch package"
author: "Henrik Olofsson and Sofie Jörgensen"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


The `apiFetch` package contains an API fetch function for accessing data from the Thenmap API (url{https://www.thenmap.net}). Thenmap is a repository for national borders. In this vignette, we will present the functionality of the `fetch()` function and visualize the borders using the Shiny Application `thenmap_viz`. 


Let us say that we are interested in data from 1906-01-20 and 2020-09-01. To obtain a list with the data we call the function `fetch()`:

```{r}
library("apiFetch")

fetch("1906-01-20")
fetch("2020-09-01")
```

Now we are going to demonstrate an application of the `apiFetch` package. Historical as well as current borders can easily be visualized by using the Shiny Application `thenmap_viz`. We select the dates 1906-01-20 and 2020-09-01, one at a time, in the Date widget.

```{r}
# Shiny stuff
```

The maps show that the borders have changes over time...blabla


