---
title: "apiFetch"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{apiFetch}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r}
library("apiFetch")
```

The `apiFetch` package contains an API fetch function for accessing data from the Thenmap API api.thenmap.net. Thenmap is a repository for geographical borders. In this vignette, we will present the functionality of the `fetch()` function and visualize the borders using the Shiny Application `thenmap_viz`.

## The API
Via the API, geojson data can be downloaded. The geojson object fetched from the API is converted to a simple features (sf) object. Simply calling `fetch()` will fetch current national borders.

Let us say that we are interested in data from 1906-01-20. To obtain a list with the data we call the function `fetch()`. As a default print method, the first ten objects are displayed.
```{r}
fetch(date_str = "1906-01-20")
```

Data can also be fetched from other url's, e.g. the Swedish counties:
```{r}
fetch(url = "http://api.thenmap.net/v2/se-4/geo/")
```
Now we are going to demonstrate an application of the `apiFetch` package. Historical as well as current borders can easily be visualized by using the Shiny application `thenmap_viz`. We select the dates 1906-01-20 and 2020-09-01, one at a time, in the Date widget.

```{r}
# shiny::runGitHub("sofiejorgensen/thenmap_viz", subdir = "thenmap_viz")
```
