---
title: "An API fetch package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{thenmap-viz}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r}
library("apiFetch")
```

The `apiFetch` package contains an API fetch function for accessing data from the Thenmap API https://www.thenmap.net. Thenmap is a repository for national borders. In this vignette, we will present the functionality of the `fetch()` function and visualize the borders using the Shiny Application `thenmap_viz`. 


Let us say that we are interested in data from 1906-01-20. To obtain a list with the data we call the function `fetch()`:

```{r}
fetch("1906-01-20")
```

Now we are going to demonstrate an application of the `apiFetch` package. Historical as well as current borders can easily be visualized by using the Shiny Application `thenmap_viz`. We select the dates 1906-01-20 and 2020-09-01, one at a time, in the Date widget.

```{r}
# Shiny stuff
```
